Gut-resident microorganisms and their genes are associated with cognition and neuroanatomy in children

### 2023-10-04 manuscript/main.tex
Subscales results

>>>>

\subsubsection*{Gut microbial taxa relate diffrentially to distinct cognitive subscales} %TODO: add numbers!

Is it possible to associate the predictive species with different components of cognition? 
After probing the aforedescribed importances of potential of taxa and ECs 
towards composite cognitive scores, we proceeded to verify if and how this relationship 
would hold for different subcomponents of the cognitive function assessment. 
We collected those in the form of the 
Mullen Scales of Early Learning (MSEL - see \textit{see Methods}). 
Taxonomic profiles coupled with demographics exhibited predictive potential towards three probed subscales, 
namely Expressive Language (EL; test-set RMSE XXX, test-set correlation YYYY), 
Gross Motor (GM; test-set RMSE XXX, test-set correlation YYYY) and 
Visual Reception (VR; test-set RMSE XXX, test-set correlation YYYY).
Between the subscales, not only the predictability (measured by the test-set figures of merit) is different,
but also the relative importances of several taxa.
Although certain species such as \textit{B. longum}, \textit{F.prausznitzii} 
have similar relative importance across all subscales, others are substantially different.
Notably, \textit{Bifidobacterium pseudocatenulatum}, \textit{B. wexlerae} and \textit{E. eligens} are
substantially more important for the prediction of EL, while
\textit{R. faecis}, \textit{S. salivarius} and \textit{F. saccharivorans} are
distinctly predictive of GM, and
\textit{Clostridium innocuum}, \textit{B. vulgatus} 
stand out on models targeting VR.
